D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-04-07 doc/proposal/proposal.tex
Proposal edit 2

\section{Objective}
    The main objective of the D.I.A.G.R.A.M. system is to:
    \begin{itemize}
        \item Develop a computer vision model to recognize handwritten diagrams.
        \item Extract relevant features from the diagrams (nodes, edges, labels).
        \item Generate equivalent code in supported languages for the recognized diagrams.
        \item Automatically parse the code to generate the formatted image of the input diagram.
    \end{itemize}

@@

\section{Constraint}
While the whole project idea could be applied to a wide variety of diagrams and languages, in order to manage the complexity we decided to impose a few theoretical constraints:

>>>>

\section{Objective}
    The main objective of the D.I.A.G.R.A.M. system is to:
    \begin{itemize}
        \item Develop a computer vision model to recognize handwritten diagrams.
        \item Extract relevant features from the diagrams (\textit{e.g.} nodes, edges, labels).
        \item Generate equivalent code in supported languages for the recognized diagrams.
        \item Automatically parse the code to generate the formatted image of the input diagram.
    \end{itemize}

@@

\section{Constraints}
While the whole project idea could be applied to a wide variety of diagrams and languages, in order to manage the complexity we decided to impose a few theoretical constraints:
